Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100 Data

### 2017-03-16 Inelastic/analysis.tex
Added appendix and rho correction

\begin{multline}
	f(cS1_{er},cS2_{er})  = {\rm exp} \Big\{ -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1_{er} - \mu_{cS1})^2}{\sigma_{cs1}^2} + \\ 
	 \frac{(cS2_{er} - \mu_{cS2})^2}{\sigma_{cs2}^2} - \frac{2\rho\cdot(cS1_{er} - \mu_{cs1}) (cS2_{er} - \mu_{cs2})} {\sigma_{cs1}\sigma_{cs2}} \Big] \Big\}
	%f(cS1,cS2) ~ = ~  \frac{1}{2 \pi \sigma_{cs1} \sigma_cs2 \sqrt{1-\rho^{2}} } exp \Big( -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1 - \hat{cS1})^2}{\sigma_{cs1}^2} \Big] \Big)
\label{f:2dgaus}
\end{multline}
where $\mu_{cS1}$ and $\mu_{cS2}$ 
represent the average observed $\rm{cS1_{er}}$ and $\rm{cS2_{er}}$ signals given a 39.6\,keV ER, $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in $\rm{cS1_{er}}$ and $\rm{cS2_{er}}$ respectively,
while $\rho$ stands for the correlation between the cS1 and cS2 signals. The detector-related light yield $L_y$  at 39.6\,keV, necessary to evaluate the average number of prompt photons detected 
($\mu_{cS1}$), is obtained from the NEST model~\cite{NEST,Geant1,Geant2} fit to data collected with several $\gamma$-lines.
%%%%% REMOVEME %%%%%%
%The average light yield at 39.6\,keV is 2.7\,PE/keV.
The same model is used to predict the charge yield at 39.6\,keV, which is then scaled according to the detector's secondary scintillation gain $Y$. 
 The latter is determined from detector's response to single electrons~\cite{SingleE}.
The energy resolution at 39.6\,keV in cS1 and cS2 has been measured to be 15.8\% and 14.7\%, respectively, and is used to extract the standard 
deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered narrow energy range) and measured
using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{241}$AmBe run. This $\gamma$-line is chosen since, unlike the 39.6\,keV line, 
it is not associated with a NR and a measure of the (cS1,cS2) correlation of a pure ER interaction is possible. The correlation coefficient however depends on energy due to 
recombination effects, its measured value at 164\,keV is then corrected based on the NEST expected recombination fractions for those energies. 
The corrected correlation coefficient is then $\rho \, = \, -0.4 \pm 0.1$.

>>>>

\begin{multline}
	f(cS1_{er},cS2_{er})  = {\rm exp} \Big\{ -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1_{er} - \mu_{cS1})^2}{\sigma_{cs1}^2} + \\ 
	 \frac{(cS2_{er} - \mu_{cS2})^2}{\sigma_{cs2}^2} - \frac{2\rho\cdot(cS1_{er} - \mu_{cs1}) (cS2_{er} - \mu_{cs2})} {\sigma_{cs1}\sigma_{cs2}} \Big] \Big\}
	%f(cS1,cS2) ~ = ~  \frac{1}{2 \pi \sigma_{cs1} \sigma_cs2 \sqrt{1-\rho^{2}} } exp \Big( -\frac{1}{2(1-\rho^2)} \Big[ \frac{(cS1 - \hat{cS1})^2}{\sigma_{cs1}^2} \Big] \Big)
\label{f:2dgaus}
\end{multline}
where $\mu_{cS1}$ and $\mu_{cS2}$ 
represent the average observed $\rm{cS1_{er}}$ and $\rm{cS2_{er}}$ signals given a 39.6\,keV ER, $\sigma_{cs1}$ and $\sigma_{cs2}$ are the standard deviation in $\rm{cS1_{er}}$ and $\rm{cS2_{er}}$ respectively,
while $\rho$ stands for the correlation between the cS1 and cS2 signals. The detector-related light yield $L_y$  at 39.6\,keV, necessary to evaluate the average number of prompt photons detected 
($\mu_{cS1}$), is obtained from the NEST model~\cite{NEST,Geant1,Geant2} fit to data collected with several $\gamma$-lines.
%%%%% REMOVEME %%%%%%
%The average light yield at 39.6\,keV is 2.7\,PE/keV.
The same model is used to predict the charge yield at 39.6\,keV, which is then scaled according to the detector's secondary scintillation gain $Y$. 
 The latter is determined from detector's response to single electrons~\cite{SingleE}.
The energy resolution at 39.6\,keV in cS1 and cS2 has been measured to be 15.8\% and 14.7\%, respectively, and is used to extract the standard 
deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is measured
using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{241}$AmBe run. This $\gamma$-line is chosen since, unlike the 39.6\,keV line, 
it is not associated with a NR and a measure of the (cS1,cS2) correlation of a pure ER interaction is possible. The correlation coefficient however depends on energy due to 
electron recombination effects, its measured value at 164\,keV is then corrected based on the NEST expected recombination fractions for those energies. 
The corrected correlation coefficient is then $\rho \, = \, -0.4 \pm 0.1$.
